### 2025-08-19 analysis.qmd
Added keyword visualisations

```{r}
#| id: preprocess
#| eval: true
#| output: asis
source('scripts/load_scopus_datasets.R') # Creates full_names dataset
source('scripts/attribute_country.R') # Add country affiliations
source('scripts/attribute_gender.R') # Adds gender attributions (precalculated with API)
source('scripts/create_keys.R') # Add keys for authors and study+author
source('scripts/clean_citations_and_OA.R') # Process citations and OA status
source('scripts/attribute_gender_diagnostics.R') # Process citations and OA status
source('scripts/export_gender_data.R')
```

@@

```{r}
#| id: geographical2
#| eval: true
#| echo: true
#| output: asis
#source('scripts/table_continent.R') # IN progress
```

@@

>>>>

```{r}
#| id: preprocess
#| eval: true
#| output: asis
source('scripts/load_scopus_datasets.R') # Creates full_names dataset
source('scripts/attribute_country.R') # Add country affiliations
source('scripts/attribute_gender.R') # Adds gender attributions (precalculated with API)
source('scripts/name_gender_fixes.R') # Fixes the gender attribution of some names manually 
source('scripts/create_keys.R') # Add keys for authors and study+author
source('scripts/clean_citations_and_OA.R') # Process citations and OA status
source('scripts/attribute_gender_diagnostics.R') # Process citations and OA status
source('scripts/export_gender_data.R')
```

@@

@@

### Keywords and gender

```{r}
#| id: keywords
#| eval: true
#| echo: true
#| fig.width: 10
#| fig.height: 6
source('scripts/keyword_analysis.R') 
```
